\normalfont \normalsize \huge Battle of Online and Offline Consumption: \\ Comparative Analysis of Amazon and Walmart Stocks

### 2017-06-18 Battle_of_Online_and_Offline_Consumption.tex
update
Updated

\documentclass[paper=a4, fontsize=11pt]{article} 
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{amstext}
\usepackage{subfigure}
\RequirePackage{graphicx}
\RequirePackage{longtable,multirow,hhline,tabularx,array}
\usepackage[english]{babel} 
\RequirePackage{colortbl,booktabs}
\linespread{1.5}

@@

On the other hand, it is also acknowledged that there are some limitations of online operations. Customers would have to wait for their orders to be received, processed, and shipped. Because they couldn't physically inspect a product before ordering, Amazon would have to make its returns and redress processes transparent and reliable, and offer other ways for consumers to learn as much about the product as possible before buying.
The task to judge the performance of online consumption against offline consumption is compelling. And the methods of judgments comparisons can be diverged. In this term paper, our group conducts time series data models with conditional heteroscedasticity, which are widely applied in financial data analysis, to depict the stock volatility of Amazon and Wal-Mart's.

@@

The descriptive statistics and time plots are shown in Table \ref{ds} and Firgure \ref{tp}.

@@

From Table \ref{ds}, we can easily see that both returns of these two stocks display an increasing trend from 2010 to 2016. However, the average log return of Amazon stock  is four times greater than Walmart stock, while the log return of Walmart stock is more stable than Amazon's. From the timeplots in Figure \ref{tp}, the log return series for both stocks appear to be relatively stationary over times, fluctuating around the mean value.

@@

\subsection{Volatility Equation}
Based on the Figure \ref{cf_AMZN}.(d), there is a sudden cutoff at lag-1 squared $a_t^2$. Hence, we entertain an ARCH(1) model and a GARCH(1,1) model for the volatility and we specify the model as the following:
\[ r_t = \mu+a_t, a_t = \sigma_t \epsilon_t \]
\[ \text{ARCH(1): } \sigma_t^2 = \alpha_0+\alpha_1 a_{t-1}^2 \]
\[ \text{GARCH(1,1): } \sigma_t^2= \alpha_0+\alpha_1 a_{t-1}^2+\beta_1 \sigma_{t-1}^2 \]
in which $\epsilon_t$, we assume as a Gaussian innovation that is independent and identically distributed follows a Normal distribution with mean zero and variance one.

@@

@@

\begin{thebibliography}{99}
\bibitem{1} hahahahahahahaha
\end{thebibliography}

>>>>

\documentclass[paper=a4, fontsize=11pt]{article} 
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{amstext}
\usepackage{subfigure}
\RequirePackage{graphicx}
\RequirePackage{longtable,multirow,hhline,tabularx,array}
\usepackage[english]{babel} 
\usepackage{indentfirst}
\RequirePackage{colortbl,booktabs}
\linespread{1.5}

@@

On the other hand, it is also acknowledged that there are some limitations of online operations. Customers would have to wait for their orders to be received, processed, and shipped. Because they couldn't physically inspect a product before ordering, Amazon would have to make its returns and redress processes transparent and reliable, and offer other ways for consumers to learn as much about the product as possible before buying.

The task to judge the performance of online consumption against offline consumption is compelling. And the methods of judgments comparisons can be diverged. In this term paper, our group conducts time series data models with conditional heteroscedasticity, which are widely applied in financial data analysis, to depict the stock volatility of Amazon and Wal-Mart's.

@@

The descriptive statistics and time plots are shown in Table \ref{ds} and Figure \ref{tp}.

@@

From Table \ref{ds}, we can see that the average log return of Amazon stock  is four times greater than Walmart stock, while the log return of Walmart stock is more stable than Amazon's. From the timeplots in Figure \ref{tp}, the log return series for both stocks appear to be relatively stationary over times, fluctuating around the mean value.

@@

\subsection{Volatility Equation}
Based on the Figure \ref{cf_AMZN}.(d), there is a sudden cutoff at lag-1 squared $a_t$. Hence, we entertain an ARCH(1) model and a GARCH(1,1) model for the volatility and we specify the model as the following:
\[ r_t = \mu+a_t, a_t = \sigma_t \epsilon_t \]
\[ \text{ARCH(1): } \sigma_t^2 = \alpha_0+\alpha_1 a_{t-1}^2 \]
\[ \text{GARCH(1,1): } \sigma_t^2= \alpha_0+\alpha_1 a_{t-1}^2+\beta_1 \sigma_{t-1}^2 \]
in which $\epsilon_t$, we assume as a Gaussian innovation that is independent and identically distributed follows a Normal distribution with mean zero and variance one.

@@

Finally, to forecast the volatility of AMZN stock, we can use the volatility equation $\sigma_t^2 = 1.02+0.129a_{t-1}^2+0.637\sigma_{t-1}^2$. The 1-step-ahead forecast is then $\sigma_{h+1}^2 = 1.02+0.129a_h^2+0.637\sigma_h^2$, where $a_h$ is the residual of the mean equation at time $h$ and $\sigma_h$ is obtained from the volatility equation. For multistep-ahead forecasts, we substitute our forecasts recursively. Table \ref{fc_amzn} shows some mean and volatility forecasts for the AMZN stock. Here, the unit for Log Return is \%.

\begin{table}
\caption{Volatility Forecasts for AMZN Stock}
  \centering
\begin{tabular}[!htbp]{c|ccccccc}
\hline Horizon & 1 & 2 & 3 & 4 & 5 & $\infty$ \\ 
\hline Log Return & 0.1367 & 0.1367 & 0.1367 & 0.1367 & 0.1367 & 0.1367 \\
Volatility & 1.8940 & 1.9410 & 1.9763 &  2.0029 & 2.0230 & 2.0876\\
\hline
\end{tabular}
\label{fc_amzn}
\end{table}

Similarly, we provide mean and volatility forecasts for the WMT stock in Table \ref{fc_wmt}.
\begin{table}
\caption{Volatility Forecasts for AMZN Stock}
  \centering
\begin{tabular}[!htbp]{c|ccccccc}
\hline Horizon & 1 & 2 & 3 & 4 & 5 & $\infty$ \\ 
\hline Log Return & 0.0240 & 0.0240 & 0.0240 & 0.0240 & 0.0240 & 0.0240 \\
Volatility & 0.8920 & 0.9563 & 0.9462 & 0.9608 & 1.0069 & 1.0338\\
\hline
\end{tabular}
\label{fc_wmt}
\end{table}

@@

\begin{thebibliography}{99}
\bibitem{book} 
Lieber, Ethan and Chad Syverson. 
\textit{Online vs Offline Competition}. 
The Oxford Handbook of the Digital Economy, 2012.
\end{thebibliography}
